Supporting information to the article\\ ``Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modeling''

### 2022-07-07 esi.tex
nex expression for c_s^prime

\begin{equation}
N_{Cl^{-}}^{(gel)} = \frac{\frac{\NA \Vout^{2}}{2} + N_{pairs} \Vgel^{2} - \frac{\Vout \sqrt{N^{{(gel)}}_{A^{-}}^{2} \Vout^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} \Vgel^{2} + 4 N_{pairs}^{2} \Vgel^{2}}}{2}}{\Vgel^{2} - \Vout^{2}}
\end{equation}

@@

Compression of the gel in infinite reservoir does not  change its salinity, on the contrary, upon compression of the gel in closed reservoir salinity of separated liquid is decreasing (supernatant salinity), using the Donnan law formulated for finite reservoir salinity can be expressed as
\begin{equation*}
    c_s^\prime = \frac{\sqrt{4\alpha^{2} c_{p}^{2} \left(1-\gamma\right)^{2} + \alpha c_{p} c_{s} \gamma^{2} + c_{s}^{2} \gamma^{2}}-\frac{\alpha c_{p} \left(1-\gamma\right)}{2} - c_{s} \left(1-\gamma\right)}{\gamma^{2} - \left(1-\gamma\right)^{2}}
\end{equation*}
where $\gamma = V_{gel}/V_0$ is relative to initial volume compression.
}
\begin{eqnarray}
    %N_{Cl^{-}}^{(gel)} = \frac{\frac{N^{{(gel)}}_{A^{-}} V_{salt}^{2}}{2} + N_{pairs} V_{gel}^{2} - \frac{V_{salt} \sqrt{N^{{(gel)}}_{A^{-}}^{2} V_{salt}^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} V_{gel}^{2} + 4 N_{pairs}^{2} V_{gel}^{2}}}{2}}{V_{gel}^{2} - V_{salt}^{2}}
    \\
    N_{Na^{+}}^{(gel)} = N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)}
    \\
    N_{Cl^{-}}^{(salt)} = N_{Na^{+}}^{(gel)} = N_{pairs} - N_{Cl^{-}}^{(gel)}
\end{eqnarray}
\subsection{Sampling routine}
Data gained from Molecular Dynamics (MD) and Monte Carlo processes (MC) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data. 
We have written a small in-house python package realizing the routine estimating mean and error for the observables provided by simulation, \ie pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size. 
Within this routine we provided the way to limit sampling procedure with some timeout value, in a way similar to described in \href{https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf}{Janke2002}

>>>>

%\begin{equation}
%N_{Cl^{-}}^{(gel)} = \frac{\frac{\NA \Vout^{2}}{2} + N_{pairs} \Vgel^{2} - \frac{\Vout \sqrt{N^{{(gel)}}_{A^{-}}^{2} \Vout^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} \Vgel^{2} + 4 N_{pairs}^{2} \Vgel^{2}}}{2}}{\Vgel^{2} - \Vout^{2}}
%\end{equation}

@@

Compression of the gel in infinite reservoir does not  change its salinity, on the contrary, upon compression of the gel in closed reservoir salinity of separated liquid is decreasing (supernatant salinity), using the Donnan law formulated for finite reservoir salinity can be expressed as
\begin{equation*}
    %c_s^\prime = \frac{\sqrt{4\alpha^{2} c_{p}^{2} \left(1-\gamma\right)^{2} + \alpha c_{p} c_{s} \gamma^{2} + c_{s}^{2} \gamma^{2}}-\frac{\alpha c_{p} \left(1-\gamma\right)}{2} - c_{s} \left(1-\gamma\right)}{\gamma^{2} - \left(1-\gamma\right)^{2}}

    c_s^\prime =\frac{- V c_{s} \left(V - V_{gel}\right) - \frac{\alpha \left(V - V_{gel}\right)}{2} + \sqrt{V^{2} V_{gel}^{2} c_{s}^{2} + V V_{gel}^{2} \alpha c_{s} + \frac{\alpha^{2} \left(V - V_{gel}\right)^{2}}{4}}}{V_{gel}^{2} - \left(V - V_{gel}\right)^{2}}

\end{equation*}
where $\gamma = V_{gel}/V_0$ is relative to initial volume compression.
}
\begin{eqnarray}
    %N_{Cl^{-}}^{(gel)} = \frac{\frac{N^{{(gel)}}_{A^{-}} V_{salt}^{2}}{2} + N_{pairs} V_{gel}^{2} - \frac{V_{salt} \sqrt{N^{{(gel)}}_{A^{-}}^{2} V_{salt}^{2} + 4 N^{{(gel)}}_{A^{-}} N_{pairs} V_{gel}^{2} + 4 N_{pairs}^{2} V_{gel}^{2}}}{2}}{V_{gel}^{2} - V_{salt}^{2}}
    \\
    N_{Na^{+}}^{(gel)} = N^{{(gel)}}_{A^{-}} + N_{Cl^{-}}^{(gel)}
    \\
    N_{Cl^{-}}^{(salt)} = N_{Na^{+}}^{(gel)} = N_{pairs} - N_{Cl^{-}}^{(gel)}
\end{eqnarray}
\subsection{Sampling routine}
Data gained from Molecular Dynamics (MD) and Monte Carlo processes (MC) are highly autocorrelated, thus we can not imply statistic developed for uncorrelated data. 
We have written a small in-house python package realizing the routine estimating mean and error for the observables provided by simulation, \ie pressure, number of particles, end-to-end distance of a chain for a given confidence level or effective sample size. 
Within this routine we provided the way to limit sampling procedure with some timeout value, in a way similar to described in \href{https://www.physik.uni-leipzig.de/~janke/Paper/nic10_423_2002.pdf}{Janke2002}
